### 2019-04-24 sections/intuition.tex
remove reference to distributed apps

Input events drive evaluation of tasks.
When the system receives a valid event, it applies this event to the current task, which results in a new task.
In this way the system communicates with the environment.
Inputs are synchronous.
We assume systems react instantaneously to each if those events.

@@

By focussing on collaboration instead of communication, \TOP leads to specifications closer to real-world workflows which, at the same time, can be used to generate distributed, multi-user applications to support such workflows.

>>>>

Input events drive evaluation of tasks.
When the system receives a valid event, it applies this event to the current task, which results in a new task.
In this way the system communicates with the environment.
Inputs are synchronous.
We assume systems react instantaneously to each of those events.

@@

By focussing on collaboration instead of communication, \TOP leads to specifications closer to real-world workflows which, at the same time, can be used to generate multi-user applications to support such workflows.
